---
output: html_document
params:
  symbol: GOOG
---

## `r params$symbol`

```{r echo=FALSE, message=FALSE}
# set up

library(xts)
library(quantmod)

prices <- getSymbols(params$symbol, auto.assign = FALSE)
move <- Cl(last(prices)) - Op(last(prices))
```

`r params$symbol` will **`r ifelse(move > 0, "increase", "decrease")`** in price during the next trading period. 

This forecast was predicted with the *recency algorithm*, a simple---probably useless---method for determining stock prices. The recency algorithm predicts that the next price movement will be in the same direction as the most recent price movement.


## Price History

The chart below is made with the `quantmod` R package, a widely used package for collecting and visualizing financial data in R. You can learn more about `quantmod` at the website [www.quantmod.com](rstudio.github.io/DT/).  

***

```{r echo=FALSE}
chartSeries(prices, theme = chartTheme("white", bg.col = "white"))
```

## Raw Data

The table below displays the daily price data for the stock. In the next section, we will learn how to make a concise, interactive table with the `DT` package, a new package for making searchable data tables. You can learn more about the `DT` package at the website [rstudio.github.io/DT/](rstudio.github.io/DT/).  

***

```{r echo=FALSE, comment=''}
DT::datatable(as.data.frame(prices)[ , 1:4])
```

